Quantifying the importance of an inference model in Bayesian phylogenetics

### 2020-03-26 supplement.tex
Create guidelines

These supplementary materials show the full pipeline and
added diagnostics for the examples in the main article.

All the figures shown in this section are shown as-is, 
without any aesthetical modifications, with the exception that the arrangement
of the sub-figures (for example, aligning true and twin tree
horizontally) is done manually.

We limited the amount of replicates by time, aiming at a duration of
24 hours per setting, when run on the computer cluster of the
University of Groningen. Due to this, for example, a run of 40 taxa only
has 6 replicates, as one run takes 4 hours.

@@

\itemize{
  \item follow the guidelines as given by BEAST2
}

>>>>

These supplementary materials show facets of \verb;pirouette; that did not
fit the main article, such as the installation and an overview of
pirouette's main functions.

Additionally, there is a guide for empicists, based on multiple experiments
that are shown here as well.

For these experiments, we limited the amount of replicates by time, 
aiming at a duration of
24 hours per setting, when run on the computer cluster of the
University of Groningen. Due to this, for example, a run of 40 taxa only
has 6 replicates, as one run takes 4 hours.

All the figures shown in this section are shown as-is, 
without any aesthetical modifications, with the exception that the arrangement
of the sub-figures in subsection \ref{subsec:main_example},
where we aligned parts of the figure by hand.

@@

From the experiments shown below, we composed some rough guidelines.
These guidelines should be treated as preliminary results, as
the total runtime of these experiments is 'only' 19 days.

\itemize{
  \item the use of 20 replicates results in decent plots
  \item the use of more taxa, counterintuitively, increases the inference error
  \item the use of longer DNA sequences, as expected, decreases the inference error
  \item {
    there is a difference when a twin alignment is selected to have
    an equal amount of mutations as the true alignment. The consequences
    of this is unknown
  }
  \item using a mutation rate less than 1.0 / crown age, decreases the
    inference error. We predict this will increase the error in the parameter
    estimation
  } 
}
